Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-11 paper.tex
over one million children -> over two million
We can use http://wiki.laptop.org/go/Deployments as a citation -- it
says "There are over 2.5 million XOs in the field as of November, 2011."
Some of those are in warehouses, but not .5 million of them.
Typo fix: "In a disconnected deployments"

% Draft 7
% "education platform" -> "literacy platform"?
\textsc{Nell} is a tablet-oriented education platform for children in
the developing world.  A novel modular narrative system guides
learning, even for children far from educational infrastructure, and
provides personalized instruction which grows with the child.
Nell's design builds on experience with the Sugar Learning
Platform~\cite{sugar}, used by over a million children around the
world.

@@

New story modules can be incorporated by visiting an internet page in
connected deployments.  In a disconnected deployments, new stories
might be distributed once a year on USB sticks, or shared from your
friends.  In a classroom environment, a teacher can share stories for
the day's lesson at the start of class.

>>>>

% Draft 7
% "education platform" -> "literacy platform"?
\textsc{Nell} is a tablet-oriented education platform for children in
the developing world.  A novel modular narrative system guides
learning, even for children far from educational infrastructure, and
provides personalized instruction which grows with the child.
Nell's design builds on experience with the Sugar Learning
Platform~\cite{sugar}, used by over two million children around the
world.

@@

New story modules can be incorporated by visiting an internet page in
connected deployments.  In disconnected deployments, new stories
might be distributed once a year on USB sticks, or shared from your
friends.  In a classroom environment, a teacher can share stories for
the day's lesson at the start of class.
